Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-10 msbr_reproc.tex

A major problem with the reprocessing method is that different nuclides have 
specific removal rates. On the one hand, if the depletion time intervals are 
very short it means specific isotope being instantly removed, and it is hard to 
obtain equilibrium composition because enormous large number of depletion 
steps. On the other hand, if the depletion calculation time interval is too 
long the results would not truly represents \gls{MSBR} conceptual design. 
Following this idea, the time interval for depletion calculations was selected 
3 days that correlate with the removal interval of $^{233}$Pa which is the 
major isotope for producing $^{233}$U. Thorium is continuously adding to 
maintain the initial mass fraction of $^{232}$ThF$_4$.

>>>>

A major problem with the reprocessing method is that different nuclides have 
specific removal rates. On the one hand, if the depletion time intervals are 
very short it means specific isotope being instantly removed, and it is hard to 
obtain equilibrium composition because enormous large number of depletion 
steps. On the other hand, if the depletion calculation time interval is too 
long the results would not truly represent the \gls{MSBR} conceptual design. 
Following this idea, the time interval for depletion calculations was selected 
as 3 days to correlate with the removal interval of $^{233}$Pa. Thorium is 
continuously added to 
maintain the initial mass fraction of $^{232}$ThF$_4$.
